Cross-relaxation in dense ensembles of NV centers and application to magnetometry

### 2022-10-20 Manuscrit Thèse/These_copie.tex
toto

\jurymember{1}{Dmitry Budker}{Professor JGU Mainz}{Rapporteur}
\jurymember{2}{Philippe Tamarat}{Professeur, Université de Bordeaux}{Rapporteur}
\jurymember{3}{Maria Chamarro}{Professeure, Sorbonne Université}{Examinateur}
\jurymember{4}{Vincent Jacques}{Dirrecteur de recherche, CNRS}{Examinateur}
\jurymember{5}{Alexandre Tallaire}{Dirrecteur de recherche, CNRS}{Examinateur}
\jurymember{6}{Gabriel Hétet}{Maitre de conférence, ENS Paris}{Directeur de thèse}
% \jurymember{9}{Prénom NOM}{Titre, établissement}{Invité}
% \jurymember{10}{Prénom NOM}{Titre, établissement}{Invité}

@@

\chapter{Diamond samples}
This appendix document the known properties of every diamond samples used in this manuscript.

@@

\chapter{Computation of $\bar \eta$}
We will discuss here the specifics to the computation of the  $\bar \eta$ factor for different geometric configurations, and how to compute the $T_1$ times in table [REF] of chapter [REF], and table [REF] of chapter [REF].

@@

\chapter{Influence of the magnetic field misalignment and laser polarization on the low field relaxation}

\section{Magnetic field alignment}
\begin{figure}[h]
\centering
\includegraphics[width=.7\textwidth]{chapter 4/Figures/alignement_rose}
\caption{PL of sample CVD-pink as a function of the magnetic field for 7 different misalignment of the field with respect to the [100] axis}
\label{alignement rose}
\end{figure}

>>>>

\jurymember{1}{Dmitry Budker}{Professor JGU Mainz}{Rapporteur}
\jurymember{2}{Philippe Tamarat}{Professeur, Université de Bordeaux}{Rapporteur}
\jurymember{3}{Maria Chamarro}{Professeure, Sorbonne Université}{Examinateur}
\jurymember{4}{Vincent Jacques}{Directeur de recherche, CNRS}{Examinateur}
\jurymember{5}{Alexandre Tallaire}{Directeur de recherche, CNRS}{Examinateur}
\jurymember{6}{Gabriel Hétet}{Maître de conférences, ENS Paris}{Directeur de thèse}
% \jurymember{9}{Prénom NOM}{Titre, établissement}{Invité}
% \jurymember{10}{Prénom NOM}{Titre, établissement}{Invité}

@@

\chapter{Diamond samples}
\label{Appendix samples}
This appendix document the known properties of every diamond samples used in this manuscript.

@@

\chapter{Computation of $\bar \eta$}
\label{Appendix eta}
We will discuss here the specifics to the computation of the  $\bar \eta$ factor for different geometric configurations, and how to compute the $T_1$ times in table [REF] of chapter [REF], and table [REF] of chapter [REF].

@@

\chapter{Influence of the magnetic field misalignment and laser polarization on the low field relaxation}
\label{Appendix autres causes}
\section{Magnetic field alignment}
\begin{figure}[h]
\centering
\includegraphics[width=.7\textwidth]{chapter 4/Figures/alignement_rose}
\caption{PL of sample CVD-pink as a function of the magnetic field for 7 different misalignment of the field with respect to the [100] axis}
\label{alignement rose}
\end{figure}
